---
title: "Introduction to the octawave Package"
author: "Katharina M. Brecht"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the octawave Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to the `octawave` package! This library is specifically designed for the simulation and visualization of three-dimensional octahedral quantum wave interferences and spatial resonance fields. 

**Scientific Foundations:** Every generated model is based on mathematically validated equations computed across a three-dimensional continuum. The underlying algorithms strictly account for multi-source wave superposition (interferences) and quantum-mechanical amplitude damping over time, transforming spatial theory into reproducible, interactive data.

Additionally, the package provides advanced functions to generate virtual Magnetic Resonance Imaging (MRI) slice scans.

This guide introduces you to the core functionalities of the package.

## 1. Load the Package

First, load the package into your current R session:

```{r setup}
library(octawave)
```

## 2. Interactive & Dynamic 3D Simulations

The package features real-time interactive environments allowing users to dynamically trigger multi-drop wave simulations and explore continuous wave progression in space:

```R
# Launch the floating 3D live landscape visualizer
floating_3d_octawave()

# Open the interactive multi-drop 3D zone for overlapping wave simulations
interactive_multi_drop_3d()

# Render the floating 3D volume model of the octahedral core in space
interactive_volume_octawave()
```

## 3. MRI Slice Simulation

The package contains specialized algorithms to compute virtual MRI scans through geometric structures. You can simulate individual slices at a specific height along the Z-axis:

```R
# Display a single MRI slice for Fullerene at height z = 0
plot_mri_fullerene(z_slice = 0.0, lang = "de")

# Display a single MRI slice for Octawave structures
plot_mri_octawave(z_slice = 0.5, lang = "de")
```

## 4. Automated Multi-Format Export

For scientific presentations, you can automatically export a complete series of slices as high-resolution PNG images and a multi-page presentation PDF with a single command:

```R
# Automatically export slice series of Fullerene and Octawave models 
# Developed by Katharina M. Brecht
export_all_mri_scans(start_z = -2.0, end_z = 2.0, schritte = 10)
```

After running this command, two new folders (`KBrecht_Fullerene_MRI_Export` and `KBrecht_Octawave_MRI_Export`) will be created in your current working directory, containing all generated image files.

