---
title: "Introduction to the octawave Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the octawave Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Welcome to the `octawave` package! This library is specifically designed for the simulation and visualization of three-dimensional octahedral quantum wave interferences and spatial resonance fields. Additionally, the package provides advanced functions to generate virtual Magnetic Resonance Imaging (MRI) slice scans.

This guide introduces you to the core functionalities of the package.

## 1. Load the Package

First, load the package into your current R session:

```{r setup}
library(octawave)
```

## 2. MRI Slice Simulation

The package contains specialized algorithms to compute virtual MRI scans through geometric structures. You can simulate individual slices at a specific height along the Z-axis:

```R
# Display a single MRI slice for Fullerene at height z = 0
plot_mri_fullerene(z_slice = 0.0, lang = "de")

# Display a single MRI slice for Octawave structures
plot_mri_octawave(z_slice = 0.5, lang = "de")
```

## 3. Automated Multi-Format Export

For scientific presentations, you can automatically export a complete series of slices as high-resolution PNG images and a multi-page presentation PDF with a single command:

```R
# Automatically export slice series of my beloved Fullerene and Octawave models 
# (Katharina M. Brecht) 
export_all_mri_scans(start_z = -2.0, end_z = 2.0, schritte = 10)
```

After running this command, two new folders (`KBrecht_Fullerene_MRI_Export` and `KBrecht_Octawave_MRI_Export`) will be created in your current working directory, containing all generated image files.

